Verifying Demonstrations

### 2018-11-27 paper/protocol.tex
removes informal adversary model, explains verification and counting, removes old strength function description, adds props reference to assumed DBAC

While there are various ways for verifying the participation count, hereafter, 
we will detail the two suggested just after \cref{DefParticipationCount}.
In the first approach, we do not trust individual witnesses, rather we \emph{assume} that it is difficult for Alice to find more than \(\theta\) witnesses willing to collude.
Thus, the strength comes from the number of witnesses and we require at least \(\theta\) witnesses to accept a participation proof as valid.
In the second approach, we trust specific witnesses, but no others.
In this case, to accept a participation proof as valid, we require at least one trusted witness, the independent journalist Jane.
It is the strength function \(\str\) of \cref{DefParticipationCount} that 
differ in the two cases.
We will first give the procedure and then how to construct the two different 
strength functions.

@@

In the case \emph{without} trusted witnesses, all the weights equal to 1 is equivalent to counting the elements in the set, 
\(\str[\prf_{\pid_j, P}] = |\prf_{\pid_j, P}|\).

In the case \emph{with} trusted witnesses, each trusted witness must inform the 
verifier of which proof shares that he or she has signed, \eg by giving a list 
of all such proof shares or digitally sign each proof share\footnote{%
  To achieve witness privacy in this situation, one could employ a group or 
  ring signature scheme for all trusted witnesses.
  Then one learns that at least one trusted witness must have been there.
}.
Then the verifier can define \[
  \str[\prf_{\pid_j, P}] = \begin{cases}
    1 & \text{if \(\exists \psh_i\in \prf_{\pid_j, P}\) that is such a proof 
      share} \\
    0 & \text{otherwise}
  \end{cases}
\] and sets \(\theta = 1\).

>>>>

% While there are various ways for verifying the participation count, hereafter, 
% we will detail the two suggested just after \cref{DefParticipationCount}.
% In the first approach, we do not trust individual witnesses, rather we \emph{assume} that it is difficult for Alice to find more than \(\theta\) witnesses willing to collude.
% Thus, the strength comes from the number of witnesses and we require at least \(\theta\) witnesses to accept a participation proof as valid.
% In the second approach, we trust specific witnesses, but no others.
% In this case, to accept a participation proof as valid, we require at least one trusted witness, the independent journalist Jane.
% It is the strength function \(\str\) of \cref{DefParticipationCount} that 
% differ in the two cases.
% We will first give the procedure and then how to construct the two different 
% strength functions.

@@

% In the case \emph{without} trusted witnesses, all the weights equal to 1 is equivalent to counting the elements in the set, 
% \(\str[\prf_{\pid_j, P}] = |\prf_{\pid_j, P}|\).

In the case of trusted witnesses, each such trusted witness must
publish or otherwise inform the 
verifier of which proof shares she has signed, \eg by giving a list 
of all such proof shares or digitally signing each proof share\footnote{
 To achieve witness privacy in this situation, one could employ a group or 
 ring signature scheme for all trusted witnesses.
 Then one learns that at least one trusted witness must have been there.
}.

Note that anyone who does the counting can choose the eligibility
criteria (time interval, location, number of regular or trusted
witnesses, who is considered to be a trusted witness) for their count
and as long as these are published along with the result, any one can
verify the correctness under those criteria.

% Then the verifier can define \[
%   \str[\prf_{\pid_j, P}] = \begin{cases}
%     1 & \text{if \(\exists \psh_i\in \prf_{\pid_j, P}\) that is such a proof 
%       share} \\
%     0 & \text{otherwise}
%   \end{cases}
% \] and sets \(\theta = 1\).
